Codebook
========
Codebook was generated on `r as.character(Sys.time())` during the same process that generated the dataset. See `run_analysis.md` or `run_analysis.html` for details on dataset creation.

Variable list and descriptions
------------------------------

Variable name       | Description
--------------------|------------
subject             | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.
activity            | Activity name
featureJerk         | Feature: Jerk signal
featureVariable     | Feature: Variable (Mean or SD)
featureAcceleration | Feature: Acceleration signal (Body or Gravity)
featureCount        | Feature: Count of data points used to compute `average`
featureInstrument   | Feature: Measuring instrument (Accelerometer or Gyroscope)
featureAxis         | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
featureDomain       | Feature: Time domain signal or frequency domain signal (Time or Freq)
featureMagnitude    | Feature: Magnitude of the signals calculated using the Euclidean norm
featureAverage      | Feature: Average of each variable for each activity and each subject

Dataset structure
-----------------

```{r}
str(dataTableTidy)
```

List the key variables in the data table
----------------------------------------

```{r}
key(dataTableTidy)
```

Show a few rows of the dataset
------------------------------

```{r}
dataTableTidy
```

Summary of variables
--------------------

```{r}
summary(dataTableTidy)
```

List all possible combinations of features
------------------------------------------

```{r}
dataTableTidy[, .N, by=c(names(dataTableTidy)[grep("^feature", names(dataTableTidy))])]
```

Save to file
------------

Save data table objects to a tab-delimited text file called `TidyDataset.txt`.

```{r save}
f <- file.path(path, "TidyDataset.txt")
write.table(dataTableTidy, f, quote=FALSE, sep="\t", row.names=FALSE)
```
